Tutorial: Quantifying Spatially Resolved Hydration Thermodynamics Using Grid Inhomogeneous Solvation Theory [Article v\versionnumber]

### 2025-05-19 manuscript/manuscript.tex
Small changes to the requirement section

\subsection{Software/system requirements}
The main implementation of GIST is part of the MD analysis software \software{cpptraj} released with AmberTools \cite{amber24, Case2023-ambertools}.
A recent version of \software{cpptraj} should be used. We recommend using at least version 6.24, which was released with AmberTools24 \cite{Case2023-ambertools}. 
An overview of how to work with \software{cpptraj} is provided in the program's documentation \cite{cpptraj_doc}, AMBER tutorials \cite{amber_tut_cpptraj} and on the AMBER-hub website \cite{amber_hub}.

@@

Furthermore, a recent Python version (3.6 or newer) should be available with the following packages installed:
\begin{itemize}
	\item \software{gisttools} (\url{https://github.com/liedllab/gisttools}, $\geq$ 0.2)
	\item \software{mdtraj} (\url{https://www.mdtraj.org/}, $\geq$ 1.9.7) \cite{McGibbon2015-mdtraj}
	\item \software{matplotlib} (\url{https://matplotlib.org/}, $\geq$ 3.7.0) \cite{Hunter2007-matplotlib}
	\item \software{numpy} (\url{https://numpy.org/}, $\geq$ 1.23.5) \cite{harris2020-numpy}
	\item \software{pandas} (\url{https://pandas.pydata.org/}, $\geq$ 1.5.3) \cite{pandas-2023_8239932}
\end{itemize}
If the reader prefers to skip the MD and GIST calculation, we also provide the GIST output files with this tutorial, such that the post-processing can be done without any expensive calculations.
Additionally, the MD simulation files and raw GIST output files can be found at \url{https://doi.org/10.48323/4mbrd-67m83}, to reproduce the results shown in this tutorial.
We additionally provide a Jupyter notebook \cite{Kluyver2016-jupyter,Granger2021-jupyter} with the presented analyses. 
For the visualization of three-dimensional contributions we require molecular visualization software that can handle \software{OpenDX} files, such as \software{PyMol} \cite{pymol} or \software{VMD} \cite{vmd}.
Most of the visualisations and results in this tutorial can also be obtained using the \software{gistpp} program, which is available from \url{https://github.com/KurtzmanLab/Gist-Post-Processing} (code and documentation). \software{Gistpp} can directly manipulate \software{OpenDX} files from the GIST output. 
Its usage and some examples were shown in a previous tutorial on GIST \cite{Ramsey2016}.
For help with the listed cpptraj commands, AMBER atom mask syntax and other AMBER-specific commands, we recommend the following webresources:\\
\begin{itemize}
\item The website https://amberhub.chpc.utah.edu/ which is managed by the Cheatham III group, 
\item The cpptraj manual at https://raw.githubusercontent.com/Amber-MD/cpptraj/master/doc/CpptrajManual.pdf 
\item and the AMBER manual \cite{amber24} at https://ambermd.org/Manuals.php.
\end{itemize}
\pagebreak %TODO: pagebreak, maybe remove these by better formatting

>>>>

\subsection{Software/system requirements}
The main implementation of GIST is part of the MD analysis software \software{cpptraj} released with AmberTools \cite{amber24, Case2023-ambertools}.
A recent version of \software{cpptraj} should be used. We recommend using at least version 6.24, which was released with AmberTools24 \cite{Case2023-ambertools}. 
An overview of how to work with \software{cpptraj} is provided in the program's documentation \cite{cpptraj_doc}, AMBER manual \cite{amber24}, AMBER tutorials \cite{amber_tut_cpptraj} and on the AMBER-hub website \cite{amber_hub}.

@@

Furthermore, a recent Python version (3.6 or newer) should be available with the following packages installed:
\begin{itemize}
	\item \software{gisttools} (\url{https://github.com/liedllab/gisttools}, $\geq$ 0.2)
	\item \software{mdtraj} (\url{https://www.mdtraj.org/}, $\geq$ 1.9.7) \cite{McGibbon2015-mdtraj}
	\item \software{matplotlib} (\url{https://matplotlib.org/}, $\geq$ 3.7.0) \cite{Hunter2007-matplotlib}
	\item \software{numpy} (\url{https://numpy.org/}, $\geq$ 1.23.5) \cite{harris2020-numpy}
	\item \software{pandas} (\url{https://pandas.pydata.org/}, $\geq$ 1.5.3) \cite{pandas-2023_8239932}
\end{itemize}
If the reader prefers to skip the MD and GIST calculation, GIST output files are provided with this tutorial, such that the post-processing can be done without any expensive calculations.
Additionally, the MD simulation files and raw GIST output files can be found at \url{https://doi.org/10.48323/4mbrd-67m83}, to reproduce the results shown in this tutorial.
We additionally provide a Jupyter notebook \cite{Kluyver2016-jupyter,Granger2021-jupyter} with the presented analyses. 
For the visualization of three-dimensional contributions we require molecular visualization software that can handle \software{OpenDX} files, such as \software{PyMol} \cite{pymol} or \software{VMD} \cite{vmd}.
Most of the visualisations and results in this tutorial can also be obtained using the \software{gistpp} program, which is available from \url{https://github.com/KurtzmanLab/Gist-Post-Processing} (code and documentation). \software{Gistpp} can directly manipulate \software{OpenDX} files from the GIST output. 
Its usage and some examples were shown in a previous tutorial on GIST \cite{Ramsey2016}.
\pagebreak %TODO: pagebreak, maybe remove these by better formatting
